A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-14 text/informal-overview.tex
分割コンパイルが失敗する

@@

\red{以下の3文をどこかに入れる必要がある}
\red{, which is called a \textit{stage variable} in \LMD.}
\red{ which is called a stage in \LMD.}
\red{Although we can apply any transition to a transition abstraction in \LTP,
	we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}

@@

First, the way of handling of constants and base types is the difference between \LMD and \LTP.
We adopt a signature $\Sigma$ to handle constants and base types.
This is because a signature simplifies kinding rules relating to type variables.
A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}

@@

Third, we also need type equivalence rules in \LMD as a dependent type system.
Although there are new primitives relating to stages which aren't in \LLF,
we can design all rules except \QPercent\ easily.
\red{design?}
\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}

>>>>

% !TEX root = ../main.tex

@@

@@

First, the way of handling of constants and type-level constants is the difference between \LMD and \LTP.
We adopt a signature $\Sigma$ to handle constants and type-level constants.
This is because a signature simplifies kinding rules relating to type variables.
A signature $\Sigma$ is composed of pairs of a base type and its kind or a constant and its type.
For example, if you want to use boolean, $\Sigma = \B::*, \text{true}:\B, \text{false}:\B$
\red{具体的な導出例を出したほうがよいか? また、なぜsimpleになるのを書くべきか?}

@@

Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
For example, vadd function, which takes a length of vector and returns addition function for vectors with the length, is following.
\newcommand{\M}{\textrm{M}}
\newcommand{\I}{\textrm{Int}}
\newcommand{\Vn}{\text{Vector}\ (\%_\alpha n)}
\begin{align*}
	  & \textbf{let}\ \text{vadd}_1 : \Pi n:\I.\TW_\alpha\Vn\to\TW_\alpha\Vn\to\TW_\alpha\Vn                 \\
	  & \hspace{7mm} = \textbf{fix}\ f.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vn.\ \lambda v_2:\TW_\alpha\Vn. \\
	  & \hspace{14mm} \textbf{if}\ n = 0                                                                     \\
	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                    \\
	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                            \\
	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                        \\
	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                        \\
	  & \hspace{21mm} \text{cons}\ (\text{head}\ t_1 + \text{head}\ t_2) (\TBL_\alpha f\ (n-1)\ t_1\ t_2))   \\
\end{align*}
\begin{align*}
	  & \textbf{let}\ \text{vadd}_\alpha : \Pi n:\I.\TW_\alpha(\Vn\to\Vn\to\Vn)                                                                      \\
	  & \hspace{7mm} = \lambda n:\I.\TB_\alpha (\lambda v_1:\Vn.\ \lambda v_2:\Vn. \TBL_\alpha \text{vadd}_1\ n\ (\TB_\alpha v_1)\ (\TB_\alpha v_2)) \\
\end{align*}
Although there are new primitives relating to stages which aren't in \LLF,
we can design all rules except \QPercent\ easily.
\red{design?}
\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}
